---
title: "ECo 602 - Analysis of Environmental Data"
subtitle: "Final Project Template: Data Analysis"
author: "Gabriel Toledo"
date: "Fall 2020"
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
editor_options:
  chunk_output_type: console
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = TRUE)
```

Everything above this line is the header.


<!-- The following text won't be displayed in your document.  It tells R how to make nicer looking buttons for your tabbed content. -->

<style type="text/css" rel="stylesheet">

.btn {
    border-width: 0 0 0 0;
    font-weight: normal;
    text-transform: none;
}

.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>


Use this document as a template to build your final project.

If you've already created the file index.Rmd in your docs folder, you can paste everything below the header into that document.

If you don't yet have an index.Rmd file, save this document as index.Rmd in the docs folder of your main class folder.

Edit this template to fill in your own content.


# Introduction

Type a brief introduction here.


# Functions 1: Data Structure Functions {.tabset .tabset-pills}

Look at the source code for the final project template, you'll notice the text:

{.tabset .tabset-pills}

This creates tabbed content for all the following sections that are one-level below.

- If you include them on a primary header (one #), all of the subsequent secondary headers will in tabs.




## `c()`

The following is the markdown text needed to reproduce my code example for `c()`:


The function `c()` *combines* or *concatenates* its arguments into a vector (a 1-dimensional data structure consisting of 1 or more elements).

- All of the elements must be of the same *type*.
  - I can't combine character and numeric types in the same call to `c()`

Here's two examples using numeric and character data types:

```{r}
# Create a vector of numbers:
num_vec  = c(1, 4, 8, 9, 13)

# Create a vector of characters:
char_vec = c("a", "fish", "data is cool")
```

I can show the contents of a vector by typing the name of the vector, or using the `print()` function.

```{r}
# Typing the name of the vector into the console prints the contents
num_vec

# The print() function accomplishes the same task:
print(char_vec)
```


## `data.frame()`

Here is more text for the data frame section!

how to subset a data frame:
-If i know the name of a column I can use the $ symbol


```{r data_fram_example_1}
#build a data frame from scratch

dat_1 = data.frame(
  letters = c("b", "w", "B"),
  numbers_1 = c(34, 6, 123454))

#I can print the contents by typing the name of the data frame
dat_1

#subset a column by name
dat_1$letters

```

## `matrix()`

Type your matrix example here.



## `length()`


## `nrow()`


## `ncol()`


## `dim()`


# Functions 2: Numerical Data Exploration  {.tabset .tabset-pills}

## `summary()`

## `mean()`

## `sd()`
 


# Functions 3: Graphical Data Exploration {.tabset .tabset-pills}

See the final project description for a list of the required functions.

## 'plot()'
I can use 'plot()' to create scatterplots!


```{r scatterplot_1, fig.asp=1.5, fig.height=10}

#load the penguins package:
require(palmerpenguins)

#using formula notation:
plot(
  bill_length_mm ~ body_mass_g, 
  data = penguins, 
  pch = 16)


```

## 'hist()'


## 'boxplot()'


## 'par()' and 'mfrow='




# Functions 4: Distribution Functions {.tabset .tabset-pills}

See the final project description for a list of the required functions.



# Functions 5: Other Functions {.tabset .tabset-pills}

See the final project description for a list of the required functions.




# Part 2: Data Anaylsis

Your data analysis materials will go here.

## Making a new code chunk

The shortcut key is ctrl-alt-i (for the code boxes)

If i press this key combo, RStudio will insert a new code chunk!



# Here is a demonstartion on how to use R Markdown

## Reading a csv file

I'm going to read some data from a csv (comma-separated-values) file.

I can use read.csv() along with the path to the file to read the data into a data.frame.

Here's an examples



```{r read_birds_data}

require(here)

dat_birds = read.csv(here("data", "hab.sta.csv"))
dat_birds <- read.csv(here("data", "hab.sta.csv"))

```


## Previewing the contents of a data.frame

I can use the head() function to print the first few lines of a data.frame.

Here's an example with the birds data



```{r head_funtion_demo}
head(dat_birds)


```

## Demo plot

I can use hist() to create a histogram:

When I plot aspect, the last column shows 400 but is only values from 350-360

```{r simple plot}
hist(dat_birds$aspect)
```


## How to customize a histogram

I can title using the argument main -




```{r custom histogram}
hist(
  dat_birds$aspect, 
  main = "histogram of study site aspect",
  breaks = 36)


```

